---
title: "Starter"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Starter}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bioseer)
```

# Preliminaries

First you should install the package before attempting to do anything with it, alongside devtools.

## Installation
```{R}
install.packages("devtools")
library("devtools")
devtools::install_github("davatana/bioseer", build_vignettes = TRUE)
library("bioseer")
```


## Loading files

Input files should be one file per feature-input combination such that each line in the file
is one residue from a sequence of amino acids with the second column being whether or not the feature
was activated on that portion of the input.

The CSV-formatted files that you wish to analyze can be placed anywhere as the function accepts a file path. 
Testing is done with the files from the insta/extdata directory. A good first step after loading your files 
is to check that they are visible to the program. The list_csv_files function can help you with this:

```{R}


```


# Analysis

To analyze the features elucidated by the SAE, the data from which was loaded into the example files, 

Now that you are ready to analyze the files, look for a visual output broken down by amino acid by doing the following.

```{R}



```